---
title: "BibTex Data"
author: 
  - name: "Thomas Pollet and Connor Malcolm"
    affiliations: 
     - name: "Northumbria University"
date: "2022-01-30"
date-modified: "`r format(Sys.time(), '%Y %B, %d')`"
title-block-banner: true
abstract: "Bilbiometric data acquired from Scopus and Web of Science and packages used."
---

## Libraries

Packages used across documents.

```{r}
#| output: false
library(tidyverse)
library(yarrr)
library(wordcloud)
library(wordcloud2)
library(bibliometrix)
library(tidyverse)
library(igraph)
library(tidygraph)
library(ggraph)
library(EGAnet)
library(papaja)
library(janitor)
library(gtools)
library(data.table)
library(readr)
library(ggplot2)
library(HiveR)
library(RBioFabric) #Installation: install.packages("remotes")
                    #remotes::install_github("wjrl/RBioFabric")
```

# Read in Data

Date of downloaded BibTex files: **16/03/2023**

BibTex files available here: (insert dropbox link here?)

## Scopus

2000 max BibTex for export

### All Open Access

Search terms for all open access, scopus:

**AFFIL(*northumbria* AND *university*) AND (*OA* (*all*)) AND (LIMIT-TO(PUBYEAR, *2023*) OR LIMIT-TO(PUBYEAR,*2022*))**

```{r}
#| output: false

scopus1000df <- convert2df(file = "scopus2000alloa.bib" , dbsource = "scopus", format = "bibtex")
scopusRESTdf <- convert2df(file = "scopusall30.bib" , dbsource = "scopus", format = "bibtex")
scopus_all_oa<- merge(scopusRESTdf, scopus1000df, all = TRUE) #Scopus has a 2000 limit for BibTex files so All Open Access needed to be downloaded into two .bib files and then merged to one


```

### Green Open Access

Search terms for all green open access, scopus:

**AFFIL(northumbria AND university) AND OA(repository) AND ( LIMIT-TO ( PUBYEAR,2023) OR LIMIT-TO ( PUBYEAR,2022))**

```{r}
#| output: false

file <- "scopusGreen.bib"

scopus_green <- convert2df(file = file , dbsource = "scopus", format = "bibtex")

```

### Green Final Open Access

Search terms for final green open access, scopus:

**AFFIL(northumbria AND university) AND OA(repositoryvor) AND ( LIMIT-TO ( PUBYEAR,2023) OR LIMIT-TO ( PUBYEAR,2022))**

```{r}
#| output: false

file <- "scopusGREENFINALOA.bib"

scopus_green_final <- convert2df(file = file , dbsource = "scopus", format = "bibtex")

```

### Green Accepted Open Access

Search terms for accepted green open access, scopus:

**AFFIL(northumbria AND university) AND OA(repositoryam) AND NOT OA(repositoryvor) AND ( LIMIT-TO ( PUBYEAR,2023) OR LIMIT-TO ( PUBYEAR,2022))**

```{r}
#| output: false

file <- "scopusGREENACCEPTEDOA.bib"

scopus_green_accepted <- convert2df(file = file , dbsource = "scopus", format = "bibtex")
```

### Not Green Open Access

Search terms for all other types of open access (gold, hybrid gold and bronze), scopus:

**AFFIL(northumbria AND university) AND NOT OA(repository) AND ( LIMIT-TO ( PUBYEAR,2023) OR LIMIT-TO ( PUBYEAR,2022))**

```{r}
#| output: false

file <- "scopusNOTGREEN.bib"

scopus_not_green <- convert2df(file = file , dbsource = "scopus", format = "bibtex")
```

## Web of Science

1000 max BibTex for export

### All Open Access

Link to query for all open access:

[**https://www.webofscience.com/wos/woscc/summary/76daec0d-afe7-4d19-9b33-afbcaf4ac927-797e5bf7/relevance/1**](link)

```{r}
#| output: false
 
wos1000df <- convert2df(file = "wosALLOA1000.bib" , dbsource = "wos", format = "bibtex")
wosRESTdf <- convert2df(file = "wosALLrest.bib" , dbsource = "wos", format = "bibtex")
wos_all_oa<- merge(wosRESTdf, wos1000df, all = TRUE)#Web of science has a 1000 limit for BibTex files so All Open Access needed to be downloaded into two .bib files and then merged to one
```

### All Green Open Access

Link to query for all open access:

[**https://www.webofscience.com/wos/woscc/summary/c535d015-7a95-4b5b-9dca-0309ca62c4f2-797fe8f3/relevance/1**](link)

```{r}
#| output: false

file <- "wosAllGreen.bib"

wos_green <- convert2df(file = file , dbsource = "wos", format = "bibtex")
```

### Not Green Open Access

Link to query for not green open access:

[**https://www.webofscience.com/wos/woscc/summary/3a3b1916-43f6-48a3-a03e-fc9e4041374b-7980065f/relevance/1**](link)

```{r}
#| output: false

file <- "wosNOTGREEN.bib"

wos_not_green <- convert2df(file = file , dbsource = "wos", format = "bibtex")
```

### Green Final Open Access

Link to query for final open access:

[**https://www.webofscience.com/wos/woscc/summary/26c9a11c-54fa-4bed-80d9-7c1592eb28c7-798058d2/relevance/1**](link)

```{r}
#| output: false

file <- "wosFinal.bib"

wos_green_final <- convert2df(file = file , dbsource = "wos", format = "bibtex")
```

### Green Accepted Open Access

Link to query for accepted open access:

[**https://www.webofscience.com/wos/woscc/summary/ff65467a-69e4-480c-8e34-bd8788e4fb56-79807445/relevance/1**](link)

```{r}
#| output: false

wos1000Accepteddf <- convert2df(file = "wosAcceptedOA1000.bib" , dbsource = "wos", format = "bibtex")
wosRESTAccepteddf <- convert2df(file = "wosAcceptedrest.bib" , dbsource = "wos", format = "bibtex")
wos_green_accepted<- merge(wosRESTAccepteddf, wos1000Accepteddf, all = TRUE)#Web of science has a 1000 limit for BibTex files so All Open Access needed to be downloaded into two .bib files and then merged to one
```
